\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.

### 2015-07-18 paper/paper 2/dc-2015.tex
3.1

At the core, we use a very simple conceptual model for constraints (see Figure \ref{fig:RDF-CV-conceptual-model}), using a small lightweight vocabulary called \emph{RDF Constraints Vocabulary (RDF-CV)}\footnote{Online available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}}.\tb{ToDo: actualize vocabulary}
\begin{figure}[H]
	\centering
		\includegraphics[width=0.80\textwidth]{images/RDF-CV.png}
	\caption{\emph{RDF Constraints Vocabulary (RDF-CV)} Conceptual Model}
	\label{fig:RDF-CV-conceptual-model}
\end{figure}

@@

The properties describing a simple constrained are very structural. The central property is the \emph{constraining element} which refers to one of 103 constraining elements described in our technical report \cite{BoschNolleAcarEckert2015}. Constraining elements are for example taken from Description Logics, another concrete example would be REGEX where a regular expression is checked against some property value. In most cases, constraining elements directly correspond to a constraint type, sometimes (as for REGEX) they are shared by several constraint types. Complex constraints again need several constraining elements to be expressed.

Irrespective of and additional to the constraining element, there are properties to describe the actual constraint, they can also be seen as parameters for the constraining element. The \emph{context class} limits the constraint to individuals of a specific class. Depending on the constraining elements, a list of \emph{classes} can be provided, for example to determine the valid classes for a value or to define a class intersection to be used in a constraint. \emph{leftProperties} and \emph{rightProperties} are lists usually containing properties the constraint is applied to. A typical example for a constraint with a right hand side list of properties would be R43, literal value comparison, where constraints like birthDate $<$ deathDate can be expressed.

Finally, the \emph{constraining value} contains a literal value to be checked against; for instance in the case of the REGEX element, it contains the regular expression to be evaluated.

>>>>

At the core, we use a very simple conceptual model for constraints (see Figure \ref{fig:RDF-CV-conceptual-model}), using a small lightweight vocabulary called \emph{RDF Constraints Vocabulary (RDF-CV)}\footnote{Online available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}}.\tb{ToDo for Thomas: actualize vocabulary}
\begin{figure}[H]
	\centering
		\includegraphics[width=0.80\textwidth]{images/RDF-CV.png}
	\caption{\emph{RDF Constraints Vocabulary (RDF-CV)} Conceptual Model}
	\label{fig:RDF-CV-conceptual-model}
\end{figure}

@@

The properties describing a simple constraint are very structural\tb{Kai, do you mean structured?}. The central property is the \emph{constraining element} which refers to one of 103 constraining elements described in our technical report \cite{BoschNolleAcarEckert2015}. Constraining elements are for example taken from Description Logics, another concrete example would be the SPARQL function REGEX where a regular expression is checked against some property value. In most cases, constraining elements directly correspond to a constraint type, sometimes (as for REGEX) they are shared by several constraint types. Complex constraints again need several constraining elements to be expressed.

Irrespective of and additional to the constraining element, there are properties to describe the actual constraint, they can also be seen as parameters for the constraining element. The \emph{context class} limits the constraint to individuals of a specific class. Depending on the constraining elements, a list of \emph{classes} can be provided, for example to determine the valid classes for a value or to define a class intersection to be used in a constraint. \emph{leftProperties} and \emph{rightProperties} are lists usually containing properties the constraint is applied to. A typical example for a constraint type with a right hand side list of properties would be \emph{literal value comparison (R-43)}, where constraints like {\small\ms{birthDate $<$ deathDate}} can be expressed. Finally, the \emph{constraining value} contains a literal value to be checked against; for instance in the case of the REGEX element, it contains the regular expression to be evaluated.
